Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2016-06-10 manuscript/manuscript_pve.Rmd
BM revisions

\
Yet another experimental approach is to reduce belowground C sink strength in tree seedlings by manipulating container size and thus rooting volume [@arp1991effects; @nesmith1998effect; @poorter2012pot]. Inadequate rooting volume can decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root].

Container size studies frequently exhibit photosynthetic down-regulation, likely as a result of sink limitation [@arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth]. A meta-analysis by Poorter et al. [-@poorter2012pot] concluded that *A*~n~ is the process likely to be the strongest affected by pot size and may best explain the effects on biomass seen in the large number of studies where containers are used. This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower assimilation rates [@robbins1988effect]. However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].  Whether down regulation of *A*~n~ and subsequent reductions of growth are quantitavely similiar has rarely been tested. Based on these previous studies, using a range of container sizes as a sink-strength manipulation provdies a way to empirically test the extent to which growth and *A*~n~ are coordinated.

>>>>

\
Yet another experimental approach is to reduce belowground C sink strength in tree seedlings by manipulating container size and thus rooting volume [@arp1991effects; @nesmith1998effect; @poorter2012pot]. Inadequate rooting volume can decrease C sink strength by progressively restricting root growth in growing plants [@thomas1991root]. In a comprehensive meta-analysis, Poorter et al. [-@poorter2012pot] demonstrated a large effect of container size on plant biomass accumulation. Photosynthetic down-regulation is generally observed in these studies [e.g. @arp1991effects; @mcconnaughay1991physical; @gunderson1994photosynthetic; @sage1994acclimation; @maina2002intra; @ronchi2006growth]. Poorter et al. [-@poorter2012pot] examined the components of relative growth rate and found the unit leaf rate to be most strongly affected. As unit leaf rate is correlated with An, they concluded that down-regulation of An may best explain the effects of container size on biomass growth.

This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower assimilation rates [@robbins1988effect]. However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does].  Whether down regulation of *A*~n~ and subsequent reductions of growth are quantitatively similar has rarely been tested. Based on these previous studies, using a range of container sizes as a sink-strength manipulation provdies a way to empirically test the extent to which growth and *A*~n~ are coordinated.
